Leadership across cultures and contexts: an exploratory analysis

### 2020-05-02 leadership_across_cultures_contexts.Rmd
Fixed a couple of bugs

To investigate variation in functions, qualities, costs, and benefits, we fit a multiple logistic mixed effects regression model of each variable as a function of subsistence strategy, continental region, leader sex, and group structure, with random intercepts for author nested within culture. We then compared the AIC value of each model to a model with only the fixed and random intercepts, retaining `r nrow(multi_aic)` models that showed at least a two point reduction in AIC value. We then created heatmaps that displayed the relative estimated marginal means for each level of these categorical explanatory variables for each outcome variable. See Figures \@ref(fig:heatmapsubsis), \@ref(fig:heatmapregion), \@ref(fig:heatmapsex), and \@ref(fig:heatmapgroups), and Tables \@ref(tab:variablevars) and \@ref(tab:universalvars).

@@

```{r leadertotalbenefits, fig.cap="Estimated marginal means of A. leader total benefits, and B. total costs, as a function of group structure, based on a logistic mixed effects regression model with random intercepts for ethnographer nested within culture. Values are on the response scale."}
# p1 <- 
#   hagenutils::ggemmeans(emmeans(m_ldrtotben, type = 'response', specs = 'group.structure2')) +
#   scale_x_continuous(limits = c(0, 0.1)) +
#   labs(title = "Total leader benefits", x = "", y = "")
# 
# p2 <- hagenutils::ggemmeans(emmeans(m_ldrtotcost, type = 'response', specs = 'group.structure2')) +
#   scale_x_continuous(limits = c(0, 0.1)) +
#   labs(title = "Total leader costs", x = "\nProbability", y = "")
# 
# p1 + p2 + plot_layout(ncol = 1) + plot_annotation(tag_levels = 'A')

@@

theplot <- all_emms(m_status_group2, c('subsistence', 'group.structure2', 'region', 'demo_sex'), 0.8, 'Predictors of leader status')

((theplots[[1]] / theplots[[2]]) | (theplots[[3]] / theplots[[4]])) + plot_annotation(title = title, tag_levels = 'A')
```

@@

```{r heatmapsubsis}

@@

```{r heatmapregion}

@@

```{r heatmapsex}

@@

```{r heatmapgroups}

>>>>

To investigate variation in functions, qualities, costs, and benefits, we fit a multiple logistic mixed effects regression model of each variable as a function of subsistence strategy, continental region, leader sex, and group structure, with random intercepts for author nested within culture. We then compared the AIC value of each model to a model with only the fixed and random intercepts, retaining `r nrow(multi_aic)` models that showed at least a two-point reduction in AIC value. We then created heatmaps that displayed the relative estimated marginal means for each level of these categorical explanatory variables for each outcome variable. See Figures \@ref(fig:heatmapsubsis), \@ref(fig:heatmapregion), \@ref(fig:heatmapsex), and \@ref(fig:heatmapgroups), and Tables \@ref(tab:variablevars) and \@ref(tab:universalvars).

@@

```{r leadertotalbenefits, fig.width=10, fig.cap="Estimated marginal means of A. leader total benefits, and B. total costs, as a function of group structure, based on a logistic mixed effects regression model with random intercepts for ethnographer nested within culture. Values are on the response scale."}
# p1 <- 
#   hagenutils::ggemmeans(emmeans(m_ldrtotben, type = 'response', specs = 'group.structure2')) +
#   scale_x_continuous(limits = c(0, 0.1)) +
#   labs(title = "Total leader benefits", x = "", y = "")
# 
# p2 <- hagenutils::ggemmeans(emmeans(m_ldrtotcost, type = 'response', specs = 'group.structure2')) +
#   scale_x_continuous(limits = c(0, 0.1)) +
#   labs(title = "Total leader costs", x = "\nProbability", y = "")
# 
# p1 + p2 + plot_layout(ncol = 1) + plot_annotation(tag_levels = 'A')

@@

theplots <- all_emms(m_status_group2, c('subsistence', 'group.structure2', 'region', 'demo_sex'), 0.8, 'Predictors of leader status')

((theplots[[1]] / theplots[[2]]) | (theplots[[3]] / theplots[[4]])) + plot_annotation(title = 'Predictors of leader status', tag_levels = 'A')
```

@@

```{r heatmapsubsis, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows, and therefore can only be compared within rows, i.e., the colors represent the relative amount of evidence across levels of the categorical predictor within the same outcome variable."}

@@

```{r heatmapregion, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

@@

```{r heatmapsex, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

@@

```{r heatmapgroups, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
